---
title: "Kmeans and Mokking Scale Analysis"
author: "Wim van der Ham"
output: github_document
---

```{r, setup, include=FALSE}
library(tidyverse)
library(broom)
library(mokken)
```

Here an example of the `kmeans()` function is shown. The `iris` dataset is divided in clusters and the clusters are compared to the `Species` column. A wrapper function is used to make it easy to try different number of clusters.

```{r}
iris_df <- as_data_frame(iris)

kmeans_for_n_clusters <- function(data, n_clusters) {
  iris_train <- data %>% 
    dplyr::select(-Species)
  
  kclust <- kmeans(iris_train, n_clusters)
  
  iris_pred <- augment(kclust, iris)
  iris_pred %>%
    count(Species, `.cluster`)
}
kmeans_for_n_clusters(iris_df, 2)
```

# Mokken scaling

[Mokken scaling](https://en.wikipedia.org/wiki/Mokken_scale) is part of the [Item response theory](https://en.wikipedia.org/wiki/Item_response_theory) and can be used to assess whether a number of items measure the same underlying concept. Here an example from the `mokken` package is used and the results are compared to the kmeans method.

```{r}
data(acl)

Communality <- acl[, 1:10]

scale <- aisp(Communality, verbose = FALSE)

Communality_t <- t(Communality)

kclust <- kmeans(Communality_t, 3)

scale
kclust
```
