---
title: "Intro Statistics Exersice"
output: html_notebook
---

# Dices

**What can you say about the difference in the mean and the standard deviation between two six-sided dices and one 12-sided dice?**

```{r}

```

# Medical Consultant

People providing an organ for donation sometimes seek the help of a special medical con-
sultant. These consultants assist the patient in all aspects of the surgery, with the goal
of reducing the possibility of complications during the medical procedure and recovery.
Patients might choose a consultant based in part on the historical complication rate of the
consultant’s clients.

One consultant tried to attract patients by noting the average complication rate for
liver donor surgeries in the US is about 10%, but her clients have had only 3 complications
in the 62 liver donor surgeries she has facilitated. She claims this is strong evidence that
her work meaningfully contributes to reducing complications (and therefore she should
be hired!).

## Simulation

**What is the point estimate of the data?**

```{r}

```

**Is it possible to assess the consultant’s claim using the data?**

**Could the low complication rate of 0.048 be due to chance? Formulate the hypotheses for this question.**

**Run 1000 simulations to get the distribution of the null hypotheses.**

```{r}

```

**Would you reject or accept the H<sub>0</sub> based on this simulation?**

## Normal model application

**Use the normal distribution to calculate the p-value and see if you draw the same conclusion.**

```{r}

```

**What can you say about the p-values found using the different methods? Can you explains that?**

# t distribution

For 150 women the weight of their babies and if they smoke or not is collected. The results are presented in the next table.

| | smoker | nonsmoker |
| --- | --- | --- |
| mean | 6.78 | 7.18 |
| std. dev. | 1.43 | 1.60 |
| sample size | 50 | 100 |

Use the t distribution to see if smoking has an influence on the baby weight. 

```{r}

```

# Confidence Interval

Calculate the 95% confidence interval for the point estimate of the previous exersice and validate of the conclusion is consistent.

```{r}

```
