---
title: "Functional Programming Answers"
output: html_notebook
---

```{r}
library(tidyverse)
library(purrr)
load("../13_functional_programming/data/swapi.rda")
load("../13_functional_programming/data/planet_lookup.rda")
load("../13_functional_programming/data/neiss_by_day.rda")
```

# How many elements are in people?

```{r}

```

# Who is the first person in people?

```{r}

```

# What is the difference between people[1] and people[[1]]?

```{r}

```

# How many starships has each character been on?

```{r}

```

# Find the name of each character homeworld

```{r}

```

# Combine names of persons with their home planet

```{r}

```

# How heavy is each person?

```{r}

```

# Use shortcuts

```{r}
map(people, "mass")

map(people, "starships") %>%
  map(length)
```

# More questions

## Which film (see films) has the most characters?

```{r}

```

## Create the planet_lookup vector from earlier

```{r}

```

## Which species has the most possible eye colors?

```{r}

```

# For DataFrames

## Make a dataframe with: name, films, episode_ids of the films, number of films, height, species

```{r}
people_df <- data_frame(
  name = 
  films = 
  height = 
  species =
)
```

# Put the film number in one string in one column

```{r}

```

# map2()

```{r}
# Explore time series -----------------------------------------------------
head(per_day[[1]])
ggplot(per_day[[1]], aes(trmt_date, count)) + geom_line()


plots <- map(per_day, ~ ggplot(.x, aes(trmt_date, count)) + geom_line())
plots

# see plots
walk(plots, print)

# save plots
walk2(paste0("./", common_codes, ".png"),
  plots, ggsave, width = 10, height = 3)

# Use map2 to add titles
plots_with_titles <- map2(per_day, common_names, 
  ~ qplot(trmt_date, count, data = .x, geom = "line") + ggtitle(.y))

plots_with_titles[[1]]

# Fit naive models
models <- map(per_day, ~ lm(count ~ month + wday, data = .x))

map2_dbl(models, per_day, modelr::rsquare)

accidents <- tibble(
  name = common_names,
  code = common_codes,
  data = per_day)

accidents %>%
  mutate(
    model = map(data, ~ lm(count ~ month + wday, data = .x)),
    rsquare = map2_dbl(model, data, modelr::rsquare)) %>%
  arrange(rsquare) %>% 
  select(name, rsquare)


# Why does rsquare take two arguments?
# so you can do this kind of thing
accidents <- accidents %>% 
  mutate(
    train = map(ts, ~ filter(.x, trmt_date < "2014-01-01")),
    test = map(ts, ~ filter(.x, trmt_date >= "2014-01-01")),
    model = map(train, ~ lm(count ~ month + wday, data = .x)))

accidents <- accidents %>% 
  mutate(
    rsquare_test = map2_dbl(model, test, modelr::rsquare)
  )

accidents %>% arrange(rsquare_test) %>% select(name, rsquare_test)
```

