---
title: "Extra Iteration Exersice"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(nycflights13)
flights <- flights %>%
  sample_n(20000)
```

1. Calculate the mean of all columns of `iris` using a `map()`
2. Make a point plot of the `arr_delay` with the following columns:
  - `dep_time`
  - `dep_delay`
  - `air_time`
  - `distance`
  
Make sure the labels are descriptive. 

# Re-coding variables

1. Set for all the columns in the data frame all the values higher than 5 to `NA`
2. Now for only the columns 1, 2 and 3.
3. The `allowed_column_values` list contains which values are allowed for every column. Try to set all the other values of the columns to `NA`

# Model

4. Look at the following (not working) code and try to understand what it should do.

```{r, eval=FALSE}
model <- glm(chemneo ~ jaar, data = df, family = binomial(link = 'logit'))
exp(confint(model))
summary(model)

model <- glm(chemneo ~ regio, data = df, family = binomial(link = 'logit'))
exp(confint(model))
summary(model)
```

5. Create an example dataframe that can be used to run this code.
6. Reduce the amount of copy-and-paste by rewriting the code.
7. Use the `broom` package to get the information from the model in a dataframe.