---
title: "Read MySQL Example"
output: html_notebook
---

```{r setup, include=FALSE}
library(odbc)
library(RMySQL)
library(tidyverse)
# httr::set_config( httr::config( ssl_verifypeer = 0L ) )
# devtools::install_github("edgararuiz/dbplot")
library(dbplot)
library(nycflights13)
```

Here a ways of connecting R to a MySQL databse is shown. First check which driver are installed on your system. If there is no MySQL driver installed it can be downloaded [here](https://dev.mysql.com/downloads/connector/odbc/).

```{r}
odbcListDrivers()
```

After that we have to be sure that the MySQL database is running locally. On ubuntu you have to run this commando: `service mysql start`

When MySQL is running we can connect to it using the `dbConnect()` function or by using the graphical interface in the connections tab.

```{r}
con <- dbConnect(MySQL(), user="root", password="test", dbname="new_schema", host="127.0.0.1")
```

When the connection is established there are 4 ways to get data from the database.

1. Using `collect()` in a `dplyr` commando
1. Using the `dbSendQuery()` function in combination with `fetch`
1. Using the `dbGetQuery()` function
1. Using an SQL code block in Rmarkdown 

```{r}
pp_tbl <- tbl(con, "paris_paintings")
# or tbl(con, in_schema("production", "paris_paintings")) if the table is not in the default schema

result <- pp_tbl %>%
  filter(lot == 2) %>%
  collect() 
  # show_query()

rs <- dbSendQuery(con, "select * from paris_paintings where lot = 2 limit 10;")
result2 <- fetch(rs, n=10)
dbClearResult(rs)

result3 <- dbGetQuery(con, "select * from paris_paintings where lot = 2 limit 10;")
```

Read using SQL directly in Rmarkdown.

```{sql, connection = con, output.var='result4'}
SELECT * FROM paris_paintings WHERE lot = 2 LIMIT 10
```

For writing data back to the database the `dbWriteTable()` can be used.

```{r}
dbWriteTable(con, name = "test_results", value = result, overwrite = TRUE) 
```

## dbplot

Using `dbplot` to make the calculations for your plots on the databse. This way the amount of data that needs to be loaded in memory is reduced.

```{r}
flights <- as_data_frame(flights)

#pp_tbl %>% 
#  dbplot_histogram(position)

flights %>% 
  dbplot_histogram(sched_dep_time)

#pp_tbl %>%
#  dbplot_raster(position, price) 

flights %>%
  filter(!is.na(arr_delay)) %>%
  dbplot_raster(arr_delay, dep_delay) 

pp_tbl %>%
  dbplot_bar(price)

pp_tbl %>%
  dbplot_line(price)
```

Use `tidypredict` to make a model and a prediction on the database level.

```{r}
library(tidypredict)

model <- pp_tbl %>%
  lm(price ~ year,  data = .)
summary(model)

tidypredict_sql(model, con)

pp_tbl %>%
  tidypredict_to_column(model) %>%
  select(price, fit, year) %>%
  mutate(diff = fit - price) 
# %>%  dbplot_histogram(diff)
```

