---
title: "Using column names in a loop"
author: "Wim van der Ham"
output: html_document
---

Here examples are shown when you want to write loops using the columns names of a data frame. Depending on the function where you want to use the variable in a different example applies. The options that are explained here are:

1. In a `dplyr` commando
1. In a `ggplot2` commando
1. In the function `lm()`

```{r setup, include=FALSE}
# source("https://install-github.me/tidyverse/rlang")
# We'll soon have a tidyeval package!
library(rlang)
library(tidyverse)
library(nycflights13)
```

## Data preparation

We use a sample of the flights data and put all the column names in the `columns` variable.

```{r}
flights_sample <- flights %>%
  sample_n(1000)

columns <- names(flights_sample)
```

## `dplyr`

For `dplyr` commandos you can use the `sym()` function together with the `!!` operator. The `qq_show()` function is also useful to debug what you are doing.

```{r, echo=TRUE, results='hide', warning=FALSE}
dfs <- vector("list", length(columns))

for (i in seq_along(columns)) {
  col <- sym(columns[[i]])
  dfs[[i]] <- flights_sample %>%
    summarise(avg = mean(!!col, na.rm = TRUE))
}

dfs
```

## `ggplot2`

For `ggplot2` this is not yet working. From version `2.3` it will as can be read [here](https://github.com/tidyverse/ggplot2/blob/master/NEWS.md). Until that time an alternative need to be used, using the `aes_string()` function. Or the `get()` function.

```{r, echo=TRUE, results='hide', warning=FALSE}
# in ggplot 2.3.0
# for (i in columns) {
#   col <- enquo(columns[[i]])
#   print(ggplot(flights_sample) +
#     geom_point(aes(arr_delay, !!as.name(col))))
# }

plot_variable <- function(variable) {
  ggplot(flights_sample) +
    geom_point(aes_string("arr_delay", variable))
}

columns %>%
  map(plot_variable)

for (i in seq_along(columns)) {
  col <- columns[[i]]
  print(ggplot(flights_sample) +
    geom_point(aes(arr_delay, get(col))))
}
```

## `lm()`

In the `lm()` it works with the `as.formula()` or `get()` function.

```{r, echo=TRUE, results='hide', warning=FALSE}
model_using_variable <- function(variable) {
  lm(as.formula(paste0("arr_delay ~ ", variable)), flights_sample)
}

columns %>%
  map(model_using_variable)

for (i in seq_along(columns)) {
  col <- columns[[i]]
  print(lm(arr_delay ~ get(col), flights_sample))
}
```
