---
title: "Functional Programming Answers"
output: html_notebook
---

```{r}
library(tidyverse)
library(purrr)
load("../functional_programming/data/swapi.rda")
load("../functional_programming/data/planet_lookup.rda")
load("../functional_programming/data/neiss_by_day.rda")
```

# How many elements are in people?

```{r}
length(people)
```

# Who is the first person in people?

```{r}
people[[1]]  # Luke!
```
# What is the difference between people[1] and people[[1]]?

```{r}
people[1] # A list inside a list

people[[1]] # A list, dropped one level of heirachy
```

# How many starships has each character been on?

```{r}
#do it for one
length(people[[1]]$starships)

#make it into a recipe by adding a tilde

#do is for all
map(people, ~ length(.x$starships))
```

# Find the name of each character homeworld

```{r}
#do it for one
planet_lookup[[people[[1]]$homeworld]]

#make it into a recipe by adding a tilde

#do is for all
map(people, ~ planet_lookup[[.x$homeworld]])
```

# Combine names of persons with their home planet

```{r}
people <- people %>%
  set_names(map_chr(people, "name"))

map(people, ~ planet_lookup[[.x$homeworld]])
```

# How heavy is each person?

```{r}
# How heavy is each character?
map_dbl(people, ~ .x[["mass"]])
# Doesn't work...because we get a string back
map(people, ~ .x[["mass"]])

# A little risky
map_dbl(people, ~ as.numeric(.x[["mass"]]))

# Probably want something like:
map_chr(people, ~ .x[["mass"]]) %>%
  readr::parse_number(na = "unknown")
```

# Use shortcuts

```{r}
map(people, "mass")

map(people, "starships") %>%
  map(length)
```

# More questions

## Which film (see films) has the most characters?

```{r}
map(films, "characters") %>%
  map_int(length) %>%
  set_names(map_chr(films, "title")) %>%
  sort(decreasing = TRUE)
```

## Create the planet_lookup vector from earlier

```{r}
planet_lookup <- map_chr(planets, "name") %>% 
  set_names(map(planets, "url"))
```

## Which species has the most possible eye colors?

```{r}
species$eye_colors

map_chr(species, "eye_colors") %>%
  strsplit(", ") %>%
  map_int(length)
# this is lazy, what about n/a and unknown?
```

# For DataFrames

## Make a dataframe with: name, films, episode_ids of the films, number of films, height, species

```{r}
people_df <- data_frame(
  name = map_chr(people, "name"),
  films = map(people, "films"),
  height = map_chr(people, "height") %>%
    readr::parse_number(na = "unknown"),
  species = map_chr(people, "species", .null = NA_character_)
)

people_df$films

film_number_lookup <- films %>%
  map_int("episode_id") %>%
  set_names(map_chr(films, "url"))

people_df <- people_df %>%
  mutate(
    film_numbers = map(films, ~ film_number_lookup[.x]),
    n_films = map_int(films, length)
  )
```

# Put the film number in one string in one column

```{r}
#do it for one
paste(people_df$film_numbers[[1]], collapse = ", ")

people_df <- people_df %>%
  mutate(films_squashed = map_chr(film_numbers, paste, collapse = ", "))
```

# map2()

```{r}
# Explore time series -----------------------------------------------------
head(per_day[[1]])
ggplot(per_day[[1]], aes(trmt_date, count)) + geom_line()


plots <- map(per_day, ~ ggplot(.x, aes(trmt_date, count)) + geom_line())
plots

# see plots
walk(plots, print)

# save plots
walk2(paste0("./", common_codes, ".png"),
  plots, ggsave, width = 10, height = 3)

# Use map2 to add titles
plots_with_titles <- map2(per_day, common_names, 
  ~ qplot(trmt_date, count, data = .x, geom = "line") + ggtitle(.y))

plots_with_titles[[1]]

# Fit naive models
models <- map(per_day, ~ lm(count ~ month + wday, data = .x))

map2_dbl(models, per_day, modelr::rsquare)

accidents <- tibble(
  name = common_names,
  code = common_codes,
  data = per_day)

accidents %>%
  mutate(
    model = map(data, ~ lm(count ~ month + wday, data = .x)),
    rsquare = map2_dbl(model, data, modelr::rsquare)) %>%
  arrange(rsquare) %>% 
  select(name, rsquare)


# Why does rsquare take two arguments?
# so you can do this kind of thing
accidents <- accidents %>% 
  mutate(
    train = map(ts, ~ filter(.x, trmt_date < "2014-01-01")),
    test = map(ts, ~ filter(.x, trmt_date >= "2014-01-01")),
    model = map(train, ~ lm(count ~ month + wday, data = .x)))

accidents <- accidents %>% 
  mutate(
    rsquare_test = map2_dbl(model, test, modelr::rsquare)
  )

accidents %>% arrange(rsquare_test) %>% select(name, rsquare_test)
```

