---
title: "Intro Statistics Exersice"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
```

# Dices

**What can you say about the difference in the mean and the standard deviation between two six-sided dices and one 12-sided dice?**

```{r}
dice_12 <- sample(1:12, 1000, replace = TRUE) %>%
  as_data_frame()
dice_66 <- sample(1:6, 1000, replace = TRUE) + sample(1:6, 1000, replace = TRUE) %>%
  as_data_frame()

ggplot(dice_12) +
  geom_bar(aes(value), stat = "count")
ggplot(dice_66) +
  geom_bar(aes(value), stat = "count")

mean(dice_12$value)
mean(dice_66$value)

sd(dice_12$value)
sd(dice_66$value)
```

# Medical Consultant

People providing an organ for donation sometimes seek the help of a special medical con-
sultant. These consultants assist the patient in all aspects of the surgery, with the goal
of reducing the possibility of complications during the medical procedure and recovery.
Patients might choose a consultant based in part on the historical complication rate of the
consultant’s clients.

One consultant tried to attract patients by noting the average complication rate for
liver donor surgeries in the US is about 10%, but her clients have had only 3 complications
in the 62 liver donor surgeries she has facilitated. She claims this is strong evidence that
her work meaningfully contributes to reducing complications (and therefore she should
be hired!).

## Simulation

**What is the point estimate of the data?**

```{r}
point_estimate <- 3 / 63
```

**Is it possible to assess the consultant’s claim using the data?**

No. The claim is that there is a causal connection, but the data are observational.
For example, maybe patients who can afford a medical consultant can afford better
medical care, which can also lead to a lower complication rate.

**Could the low complication rate of 0.048 be due to chance? Formulate the hypotheses for this question.**

**H<sub>0</sub>**: There is no association between the consultant’s contributions and the clients’ complication rate. That is, the complication rate for the consultant’s clients is equal to the US average of 10%. In statistical language, p = 0.10. 

**H<sub>A</sub>**: Patients who work with the consultant have a complication rate different than 10%, i.e. p != 0.10.

**Run 1000 simulations to get the distribution of the null hypotheses.**

```{r}
simulated_point_estimates <- 
  data_frame(value = seq(1:1000)) %>%
  mutate(value = 1:1000 %>%
    map_dbl(function(i) {
      sum(
        runif(63) < 0.1
      ) / 63
    }))
mean(simulated_point_estimates$value)

ggplot(simulated_point_estimates) +
  geom_histogram(aes(value), bins = 50) +
  geom_vline(xintercept = point_estimate) +
  labs(title = "Difference in success rates")

p_value_sim <- (sum(simulated_point_estimates$value <= point_estimate) * 2) / 1000
```

**Would you reject or accept the H<sub>0</sub> based on this simulation?**

`r p_value_sim` > 0.05 so we cannot reject the **H<sub>0</sub>**

## Normal model application

**Use the normal distribution to calculate the p-value and see if you draw the same conclusion.**

```{r}
# Calculate the standard deviation
SE <- sqrt((0.1 * (1 - 0.1) / 63))
# Calculate the Z-score
Z <- (0.1 - point_estimate) / SE
# Calculate the p-value
p_value_norm <- (1- pnorm(Z, 0, 1)) * 2
```

`r p_value_norm` > 0.05 so we cannot reject the **H<sub>0</sub>**

**What can you say about the p-values found using the different methods? Can you explains that?**

They are very different because the distribution is skewed and therefore the normal distribution method cannot be used here.

# t distribution

For 150 women the weight of their babies and if they smoke or not is collected. The results are presented in the next table.

| | smoker | nonsmoker |
| --- | --- | --- |
| mean | 6.78 | 7.18 |
| std. dev. | 1.43 | 1.60 |
| sample size | 50 | 100 |

Use the t distribution to see if smoking has an influence on the baby weight. 

```{r}
point_estimate <- 7.18 - 6.78
SE <- sqrt((1.60^2 / 100) + (1.43^2 / 50))
t <- point_estimate / SE
df <- min((50 - 1), (100 - 1))
p_value <- (1 - pt(t, df)) * 2
p_value < 0.05
```

# Confidence Interval

Calculate the 95% confidence interval for the point estimate of the previous exersice and validate of the conclusion is consistent.

```{r}
point_estimate - 1.96 * SE
point_estimate + 1.96 * SE
```
