---
title: "Funnel plot"
output: github_document
---

A [funnel plot](https://en.wikipedia.org/wiki/Funnel_plot) is a plot that shows how much a single observation is deviated from the total mean. Also a confidence interval is show so you can see if the deviation of an observation is significant. The confidence interval depends on the number of observations. 

# Dummy Data

First a sample data set is created. This example is about patients who have some treatment in a hospital and after this treatment have an event or not. Event can be complication death or something else depending on the application.

```{r, include=FALSE}
library(tidyverse)
```

```{r}
df <- tibble(
  patient_id = 1:100,
  hospital_id = sample(15, 100, replace = TRUE),
  event = rep(0:1, 50)
)
df
```

From this data the total event ratio can be calculated like:

```{r}
total_event_ratio <- mean(df$event)
total_event_ratio
```

Besides the total event rate we also need to know the event rate per hospital. So we can compare hospitals with each other an with the global mean. We create a different data frame for this:

```{r}
df_event_rate <- df %>%
  group_by(hospital_id) %>%
  summarise(
    total_patients = n(),
    total_events = sum(event)
  ) %>%
  mutate(event_rate = total_events / total_patients)
df_event_rate
```

Now we want to calculate the confidence intervals. First we specify the range over which we calculate the confidence intervals.

```{r}
n_patients_seq <- seq(0.1, max(df_event_rate$total_patients) + 1, by = 0.1)
n_patients_seq
```

Using this range and using the [formula](https://www.mathsisfun.com/data/confidence-interval.html) for calculating confidence intervals we can make a new data frame:

```{r}
df_conf <- tibble(
  n_patients = n_patients_seq,
  conf_upper = total_event_ratio + 1.96 * (sd(df$event) / sqrt(n_patients)),
  conf_lower = total_event_ratio - 1.96 * (sd(df$event) / sqrt(n_patients))
)
df_conf
```

Combining all this into one graph with different layers gives us the result we want.

```{r}
ggplot() +
  geom_ribbon(aes(x = n_patients_seq, ymin = conf_lower, ymax = conf_upper), df_conf, fill = "grey70") +
  geom_hline(yintercept = total_event_ratio, linetype = 4) +
  geom_point(aes(total_patients, event_rate), df_event_rate) + 
  coord_cartesian(ylim = c(0, 1)) +
  labs(
    title = "Hospital event rates for different sizes",
    x = "Hospital size",
    y = "Event rate"
  )
```
