---
title: "Function and Iteration Practice Answers"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(broom)
library(gapminder)
library(nycflights13)
# sample dataset to make plots faster
flights <- as_data_frame(flights) %>%
  sample_n(1000)
gapminder <- as_data_frame(gapminder)
```

# Gapminder

1. Make a linear model to predict the `pop`, population, depending on `year` for Afghanistan

```{r}

```

2. Get the `r.squared` from this model and the slope.

```{r}

```

3. Plot the model and the original data in one graph.

```{r}

```

4. Make a linear model for all the countries and select the countries with the lowest `r.squared`

```{r}

```

5. Show the growth of the 5 countries with the highes slope in one graph

```{r}

```

6. Use nest to calculate the mean of all columns per species

```{r}

```

# Flights exploration plots

2. Make a linear model between the defined variables and `arr_delay` and select the coefficients of the model with the highst `r.squared`

```{r}
columns <- c("dep_time", "sched_dep_time", "arr_time", "sched_arr_time")

```
