---
title: "Iteration"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
load("../../datasets/swapi.rda")
load("../../datasets/planet_lookup.rda")
```

# How many elements are in people?

```{r}
length(people)
```

# Who is the first person in people?

```{r}
head(people, 1)
people[[2]]$name
```

# What is the difference between people[1] and people[[1]]?

```{r}
people[[1]]$starships
length(people[[1]][["starships"]])


people_small <- head(people)

count_startships <- function(x) {
  #print(x)
  #print("---")
  #print(x$starships)
  #print("---")
  #print(x[["starships"]])
  #print("---")
  print(length(x[["starships"]]))  
}
count_startships(people[["Luke Skywalker"]])

map(people_small, count_startships)

```

# How many starships has each character been on?

```{r}

```

# Find the name of each characters homeworld

```{r}
map(people, "homeworld")
```

# Combine names of persons with their home planet

Use the `set_names()` function.

```{r}

```

# How heavy is each person?

```{r}

```

# Which film (see films) has the most characters?

```{r}

```

# Create the planet_lookup vector
# names are url
# values are planet names
# list("http://swapi.co/api/planets/2/" = "Alderaan")

```{r}

```

# Which species has the most possible eye colors?

```{r}

```
