---
title: "Poisson Distribution"
author: "Wim van der Ham"
date: "3/9/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(glm2)
knitr::opts_chunk$set(echo = TRUE)
```

# Calculating Probabilities

The [poisson distribution](https://en.wikipedia.org/wiki/Poisson_distribution) is a discrete probability distribution that expresses the probability of a given number of events occurring in a fixed interval of time or space if these events occur with a known constant rate and independently of the time since the last event.

For example the number of goals during a soccer match. During the World Cup of 2014 the average number of goals per game was 2,5. Using this average and the poisson distribution you can calculate the probability of exactly 2 goals in a match:

```{r}
dpois(2, lambda = 2.5)
```

Or calculate the probability of 1 or less goals:

```{r}
ppois(1, lambda = 2.5)
```

# Modeling

The poisson distribution can also be used to model. In the following example the number of satellites depends on the width of the crab.

```{r}
ggplot(crabs) +
  geom_point(aes(Width, Satellites))
```

We can try to model this using the poisson distribution:

```{r}
model = glm(Satellites ~ Width, crabs, family = poisson(link = log))
summary(model)
```

And check if the fit is good:

```{r}
crabs <- crabs %>%
  mutate(fitted = model$fitted)

ggplot(crabs) +
  geom_point(aes(Width, Satellites), color="blue") +
  geom_point(aes(Width, fitted), color="red")
```

Using the coefficient form the model we can calculate the number of satellites for a specific height:

```{r}
exp(-3.30 + 0.164 * 25)
```

