---
title: "Function and Loop Cases"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(gapminder)
library(nycflights13)
# sample dataset to make plots faster
flights <- as_data_frame(flights) %>%
  sample_n(1000)
gapminder <- as_data_frame(gapminder)
```

# Functions

```{r, eval=FALSE}
print(x)

x <- "hallo"
print(x)

print_x <- function() {
  print(x)
}
print_x
print_x()

print_a <- function() {
  print(a)
}
print_a()

print_input <- function(input) {
  print(input)
}
print_input()

print_input("test")
print_input(x)

print_inputs <- function(a) {
  print(a)
  print(b)
}

print_inputs(x)

b <- "b"
print_inputs(x)

print_inputs(x)

return_sum <- function(a, b) {
  a + b
}
result <- return_sum(2, 3)

calc_sum_multi <- function(a, b) {
  a + b
  a * b
}
result <- calc_sum_multi(2, 3)

calc_sum_multi <- function(a, b) {
  list(
    a + b,
    a * b  
  )
}
result <- calc_sum_multi(2, 3)
result[[1]]

calc_sum_multi <- function(a, b) {
  list(
    'sum' = a + b,
    'multi' = a * b  
  )
}
result <- calc_sum_multi(2, 3)
result[['sum']]
```

# Gapminder

1. Make a linear model to predict the `pop`, population, depending on `year` for Afghanistan

```{r}

```

2. Get the `r.squared` from this model and the slope.

```{r}

```

3. Plot the model and the original data in one graph.

```{r}

```

4. Make a linear model for all the countries and select the 5 with the largest slope and with the lowest `r.squared`

```{r}

```

# Iris exploration

1. Calculate the mean of all columns

```{r}

```

2. Calculate the mean for all columns per `Species`

```{r}

```

1. What if there where 50 columns in your data...

# Flights exploration plots

1. Make a point plot of the `arr_delay` with the following columns:
  - `dep_time`
  - `dep_delay`
  - `air_time`
  - `distance`
  
```{r}

```

2. Make a linear model between the priviously mentioned variables and `arr_delay` and select the coefficients of the model with the highst `r.squared`

```{r}

```

# Age calculations

1. For the 3 data frames that are given you want to add a column `age` that calculates the age based on the current year. Also set `age` to `NA` when people are older than 130 and with a negative age.

1. Set `age` to `NA` when `age` is lower than 18.

```{r}
df1 <- tibble(
  geboortejaar = c(1986, 1987, 19880)
)
df2 <- tibble(
  geboortejaar = c(1989, 1990, 19910)
)
df3 <- tibble(
  geboortejaar = c(1992, 1993, 19940)
)
```

3. Now you want to do the same but the `geboortejaar` colomn has a different name in every data frame.

```{r}
df1 <- tibble(
  geboortejaar = c(1986, 1987, 1988)
)
df2 <- tibble(
  gebjaar = c(1989, 1990, 1991)
)
df3 <- tibble(
  born = c(1992, 1993, 1994)
)
```

4. What if you have 50 data frames...

```{r}

```

# Re-coding variables

1. Set for all the columns in the data frame all the values higher than 5 to `NA`

```{r}
df <- tibble(
  c1 = seq(10),
  c2 = seq(10),
  c3 = seq(10),
  c4 = seq(10),
  c5 = seq(10),
  c6 = seq(10),
  c7 = seq(10),
  c8 = seq(10),
  c9 = seq(10),
  c10 = seq(10)
)
df
```

2. Now for only the columns 1, 2 and 3.

```{r}

```

3. The `allowed_column_values` list contains which values are allowed for every column. Try to set all the other values of the columns to `NA`

```{r}
allowed_column_values = list(
  seq(1), 
  seq(2),
  seq(3),
  seq(4),
  seq(5),
  seq(6), 
  seq(7),
  seq(8),
  seq(9),
  seq(10)
) %>%
  set_names(colnames(df))
allowed_column_values
```

