---
title: "rvest exersice"
output: html_notebook
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
```

```{r imdb_top_250}
page <- read_html("http://www.imdb.com/chart/top")
titles <- page %>%
  html_nodes(".titleColumn a") %>%
  html_text()
years <- page %>%
  html_nodes(".secondaryInfo") %>%
  html_text() %>%
  str_replace("\\(", "") %>% # remove (
  str_replace("\\)", "") %>% # remove )
  as.numeric()
scores <- page %>%
  html_nodes("strong") %>%
  html_text() %>%
  as.numeric()
imdb_top_250 <- data_frame(
  title = titles, 
  year = years, 
  score = scores[5:254]
  )
imdb_top_250 <- imdb_top_250 %>%
  mutate(
    rank = 1:nrow(imdb_top_250)
  )
```

# Which movies from 1995 are on the list?

```{r}
imdb_top_250 %>%
  filter(year == 1995)
```

# Which year has the most movies on this list?

```{r}
imdb_top_250 %>% 
  group_by(year) %>%
  summarise(total = n()) %>%
  arrange(desc(total)) %>%
  head(5)
```

# What is the average score per year?

```{r}
imdb_top_250 %>% 
  group_by(year) %>%
  summarise(avg_score = mean(score)) %>%
  ggplot(aes(y = avg_score, x = year)) +
    geom_point() +
    geom_smooth(method = "lm") +
    xlab("year")
```

# Exercise

1. Scrape http://www.imdb.com/chart/tvmeter 100 rows and 4 columns: `rank`, `movie name`, `year` and `rating`

1. For the first three movies scrape their pages for the following information.
  - How many episodes so far
  - First five plot keywords
  - Genres
  - Runtime
  - Country
  - Language

```{r imdb_100}
page <- read_html("http://www.imdb.com/chart/tvmeter")
titles <- page %>%
  html_nodes(".titleColumn a") %>%
  html_text()
years <- page %>%
  html_nodes(".secondaryInfo") %>%
  html_text() %>%
  str_replace("\\(", "") %>% # remove (
  str_replace("\\)", "") %>% # remove )
  as.numeric()
scores <- page %>%
  html_nodes("strong") %>%
  html_text() %>%
  as.numeric()
seq1 <- seq(1,45,2)
seq2 <- seq(46,140,2)
seq3 <- seq(141,187,2)
seq4 <- seq(188,197,2)
years <-years[c(seq1, seq2, seq3, seq4)]
imdb_100 <- data_frame(
  title = titles, 
  year = years, 
  score = scores[c(5:97, 1, 98:103)]
  )
imdb_100 <- imdb_100 %>%
  mutate(
    rank = 1:nrow(imdb_100)
  )
```

```{r}
page <- read_html("http://www.imdb.com/title/tt4574334/")
n_episodes <- page %>%
  html_nodes(".bp_sub_heading") %>%
  html_text() %>%
  str_replace(" episodes", "") %>%
  as.numeric()
first_5_keywords <- page %>%
  html_nodes(".see-more") %>%
  html_nodes(".itemprop") %>%
  html_text()
genres <- page %>%
  html_nodes(".subtext") %>%
  html_nodes(".itemprop") %>%
  html_text()
```

# Next Step

Automate scraping all the movies on this list.
