---
title: "Tidy evaluation Practice"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(nycflights13)
library(lubridate)
```

# Data preparation

We use a sample of the flights data and put all the column names in the columns variable.

```{r}
flights_sample <- flights %>%
  sample_n(1000)

columns <- names(flights_sample)
```

1. Write a function that plots the `arr_delay` against an other variable given by the user as an argument.

```{r}
plot_arr_delay_variable <- function(data, variable) {
  variable <- enquo(variable)
  
  ggplot(data) +
    geom_point(aes(arr_delay, !!variable))
}
plot_arr_delay_variable(flights_sample, dep_delay)
```


2. Write a for loop that calculates the mean value of every column in the data set.

```{r}
dfs <- vector("list", length(columns))

for (i in seq_along(columns)) {
  col <- sym(columns[[i]])
  dfs[[i]] <- flights_sample %>%
    summarise(avg = mean(!!col, na.rm = TRUE))
}

set_names(dfs, columns)

flights_sample %>%
  map_df(mean)
```

3. Write a function that converts one of the columns `dep_time`, `arr_time`, `sched_dep_time` or `sched_arr_time` to a date time object.

```{r}
make_datetime_column <- function(df, time_column) {
  
  time_column <- enquo(time_column)
  
  df %>%
    mutate(
      dep_time = make_datetime(
        year, month, day, 
        !!time_column %/% 100, !!time_column %% 100
      )
    )
}

flights_dt <- flights %>%
  make_datetime_column(dep_time)

make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

flights_df2 <- flights %>%
  mutate_at(
    vars(ends_with("time")), 
    funs(make_datetime_100(year, month, day, .))
  )
```
