---
title: "Function and Loop Cases"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(gapminder)
library(nycflights13)
# sample dataset to make plots faster
flights <- as_data_frame(flights) %>%
  sample_n(1000)
gapminder <- as_data_frame(gapminder)
```

# Functions

```{r, eval=FALSE}
print(x)

x <- "hallo"
print(x)

print_x <- function() {
  print(x)
}
print_x
print_x()

print_a <- function() {
  print(a)
}
print_a()

print_input <- function(input) {
  print(input)
}
print_input()

print_input("test")
print_input(x)

print_inputs <- function(a) {
  print(a)
  print(b)
}

print_inputs(x)

b <- "b"
print_inputs(x)

print_inputs(x)

return_sum <- function(a, b) {
  a + b
}
result <- return_sum(2, 3)

calc_sum_multi <- function(a, b) {
  a + b
  a * b
}
result <- calc_sum_multi(2, 3)

calc_sum_multi <- function(a, b) {
  list(
    a + b,
    a * b  
  )
}
result <- calc_sum_multi(2, 3)
result[[1]]

calc_sum_multi <- function(a, b) {
  list(
    'sum' = a + b,
    'multi' = a * b  
  )
}
result <- calc_sum_multi(2, 3)
result[['sum']]
```

# Gapminder

1. Make a linear model to predict the `pop`, population, depending on `year` for Afghanistan

```{r}
afg <- gapminder %>%
  filter(country == "Afghanistan")

model <- lm(pop ~ year, afg)
```

2. Get the `r.squared` from this model and the slope.

```{r}
summary(model)$r.squared
coef(model)
```

3. Plot the model and the original data in one graph.

```{r}
ggplot(afg) +
  geom_line(aes(year, pop)) +
  geom_abline(intercept = coef(model)[1], slope = coef(model)[2], color = "red")
```

4. Make a linear model for all the countries and select the 5 with the largest slope and with the lowest `r.squared`

```{r}
nested_gapminder <- gapminder %>%
  group_by(country) %>%
  nest() %>%
  mutate(
    model = map(data, ~lm(pop ~ year, .x)),
    r.squared = map_dbl(model, ~summary(.x)$r.squared),
    slope = map_dbl(model, ~ coef(.x)['year']),
    plot = map2(data, model, ~ ggplot(.x) +
      geom_line(aes(year, pop)) +
      geom_abline(intercept = coef(.y)[1], slope = coef(.y)[2], color = "red")),
    plot = map2(plot, country, ~.x + labs(title = .y))
  )

nested_gapminder %>%
  arrange(desc(slope)) %>%
  head(5) %>%
  pluck("plot")
```

```{r}
nested_gapminder %>%
  arrange(desc(slope)) %>%
  head(5) %>%
  unnest(data) %>%
  ggplot() +
  geom_line(aes(year, pop, color = country))
```

```{r}
nested_gapminder %>%
  arrange(r.squared) %>%
  head(5) %>%
  unnest(data) %>%
  ggplot() +
  geom_line(aes(year, pop, color = country))
```

# Iris exploration

1. Calculate the mean of all columns

```{r}
iris %>%
  map_df(mean)
```

2. Calculate the mean for all columns per `Species`

```{r}
iris %>%
  group_by(Species) %>%
  summarise_all(mean)
```


```{r}
nested_iris <- iris %>%
  group_by(Species) %>%
  nest() %>%
  mutate(
    means = map(data, ~summarise_all(.x, mean))
  )
nested_iris %>%
  unnest(means)
```

1. What if there where 50 columns in your data...

# Flights exploration plots

1. Make a point plot of the `arr_delay` with the following columns:
  - `dep_time`
  - `dep_delay`
  - `air_time`
  - `distance`
  
```{r}
columns <- c("dep_time", "dep_delay", "air_time", "distance")

plot_arr_delay <- function(column) {
  column <- sym(column)
  ggplot(flights) +
    geom_point(aes(!!column, arr_delay))
}

map(columns, plot_arr_delay)
```

2. Make a linear model between the priviously mentioned variables and `arr_delay` and select the coefficients of the model with the highst `r.squared`

```{r}
get_r_coef <- function(column) {
  model <- lm(as.formula(paste0("arr_delay ~ ", column)), flights)
  tibble(
    "variable" = column,
    "r.squared" = summary(model)$r.squared,
    "coefs" = list(coef(model))
  )
}
models <- map_df(columns, get_r_coef)

plot_arr_delay_with_model <- function(column, coefs) {
  column <- sym(column)
  ggplot(flights) +
    geom_point(aes(!!column, arr_delay)) +
    geom_abline(intercept = coefs[1], slope = coefs[2], color = "red")
}
map2(models$variable, models$coefs, ~plot_arr_delay_with_model(.x, .y))
```

# Age calculations

1. For the 3 data frames that are given you want to add a column `age` that calculates the age based on the current year. Also set `age` to `NA` when people are older than 130 and with a negative age.

1. Set `age` to `NA` when `age` is lower than 18.

```{r}
df1 <- tibble(
  geboortejaar = c(1986, 1987, 19880)
)
df2 <- tibble(
  geboortejaar = c(1989, 1990, 19910)
)
df3 <- tibble(
  geboortejaar = c(1992, 1993, 19940)
)

calculate_age <- function(df) {
  df1 %>%
    mutate(
      age = year(now()) - geboortejaar,
      age = if_else(age < 130 & age > 0, age, NA_real_)
    )
}

df1 <- df1 %>%
  calculate_age()
df2 <- df2 %>%
  calculate_age()
df3 <- df3 %>%
  calculate_age()
```

3. Now you want to do the same but the `geboortejaar` colomn has a different name in every data frame.

```{r}
df1 <- tibble(
  geboortejaar = c(1986, 1987, 1988)
)
df2 <- tibble(
  gebjaar = c(1989, 1990, 1991)
)
df3 <- tibble(
  born = c(1992, 1993, 1994)
)

calculate_age <- function(df, birth_year_column) {
  birth_year_column <- enquo(birth_year_column)
  df %>%
    mutate(
      age = year(now()) - !!birth_year_column,
      age = if_else(age < 130 & age > 0, age, NA_real_)
    )
}

df1 <- df1 %>%
  calculate_age(geboortejaar)
df2 <- df2 %>%
  calculate_age(gebjaar)
df3 <- df3 %>%
  calculate_age(born)
```

4. What if you have 50 data frames...

```{r}
df_list <- list(df1, df2, df3)
birth_year_column_list <- c(quote(geboortejaar), quote(gebjaar), quote(born))
birth_year_column_list <- map(c("geboortejaar", "gebjaar", "born"), sym)

df_list <- df_list %>%
  map2(birth_year_column_list, calculate_age)
```

# Re-coding variables

1. Set for all the columns in the data frame all the values higher than 5 to `NA`

```{r}
df <- tibble(
  c1 = seq(10),
  c2 = seq(10),
  c3 = seq(10),
  c4 = seq(10),
  c5 = seq(10),
  c6 = seq(10),
  c7 = seq(10),
  c8 = seq(10),
  c9 = seq(10),
  c10 = seq(10)
)
df
```

```{r}
df_clean <- df %>%
  map_df(~ if_else(.x > 5, NA_integer_, .x))
df_clean
```

```{r}
df_clean <- df %>%
  mutate_all(
    function(x) if_else(x > 5, NA_integer_, x)
  )
df_clean
```

2. Now for only the columns 1, 2 and 3.

```{r}
df_clean <- df %>%
  mutate_at(
    vars(1:3),
    function(x) if_else(x > 5, NA_integer_, x)
  )
df_clean
```

3. The `allowed_column_values` list contains which values are allowed for every column. Try to set all the other values of the columns to `NA`

```{r}
allowed_column_values = list(
  seq(1), 
  seq(2),
  seq(3),
  seq(4),
  seq(5),
  seq(6), 
  seq(7),
  seq(8),
  seq(9),
  seq(10)
) %>%
  set_names(colnames(df))

recode <- function(column, allowed_values) {
  if_else(column %in% allowed_values, column, NA_integer_)
}

names <- colnames(df)
recode(df[[names[1]]], allowed_column_values[[names[1]]])

df_clean <- names %>%
  map(~ recode(df[[.x]], allowed_column_values[[.x]])) %>%
  set_names(names) %>%
  as_data_frame()
df_clean
```

