---
title: "Functions Exersice Answers"
output: html_notebook
---

2. Create a function that calculates the percentages of 0's in a vector.

```{r}
calc_perc_0 <- function(x) {
  sum(x == 0) / length(x) * 100
}
calc_perc_0(c(0, 1, 2, 2))
```

3. Create a function that has an extra argument and calculates the percentage of that argument in the vector.

```{r}
calc_perc_element <- function(x, element) {
  sum(x == element) / length(x) * 100
}
calc_perc_element(c(0, 1, 2, 2), 2)
```

4. Add an argument to the function that determines how to deal with `NA`'s.
5. Are there arguments that should have a default value? If so give them the correct one.

```{r}
calc_perc_element <- function(x, element, na.rm = FALSE) {
  sum(x == element, na.rm = na.rm) / length(x) * 100
}
calc_perc_element(c(0, 1, 2, 2, NA), 2, na.rm = TRUE)
```

6. Extend the function before so that is returns a percentage and the number of `NA`'s.

```{r}
calc_perc_element <- function(x, element, na.rm = FALSE) {
  perc <- sum(x == element, na.rm = na.rm) / length(x) * 100
  n_missings <- sum(is.na(x))
  list("perc" = perc, "n_missings" = n_missings)
}
calc_perc_element(c(0, 1, 2, 2, NA), 2, na.rm = TRUE)
```

