---
title: "Extra Iteration Exersice Answers"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
flights <- flights %>%
  sample_n(20000)
```

1. Calculate the mean of all columns of `iris` using a `map()`

```{r}
iris %>%
  map_df(mean)
```

2. Make a point plot of the `arr_delay` with the following columns:
  - `dep_time`
  - `dep_delay`
  - `air_time`
  - `distance`
  
Make sure the labels are descriptive. 
  
```{r}
columns <- c("dep_time", "dep_delay", "air_time", "distance")

flights_plot_columns <- flights %>%
  select(columns)

point_plot <- function(column, x_label) {
  ggplot(flights) +
    geom_point(aes(column, arr_delay)) +
    labs(x = x_label)
}

map2(flights_plot_columns, columns, point_plot)

point_plot <- function(column) {
  ggplot(flights) +
    geom_point(aes(.data[[column]], arr_delay)) 
}

map(columns, point_plot)
```

# Re-coding variables

1. Set for all the columns in the data frame all the values higher than 5 to `NA`

```{r}
df <- tibble(
  c1 = seq(10),
  c2 = seq(10),
  c3 = seq(10),
  c4 = seq(10),
  c5 = seq(10),
  c6 = seq(10),
  c7 = seq(10),
  c8 = seq(10),
  c9 = seq(10),
  c10 = seq(10)
)
df
```

```{r}
recode <- function(x) {
  if_else(x > 5, NA_integer_, x)
}

df_clean <- df %>%
  map_df(recode)
df_clean
```

```{r}
df_clean <- df %>%
  mutate_all(recode)
df_clean
```

2. Now for only the columns 1, 2 and 3.

```{r}
df_clean <- df %>%
  mutate_at(vars(1:3), recode)
df_clean

recode2 <- function(x) {
  if_else(x > 6, NA_integer_, x)
}

df_clean <- df %>%
  mutate_at(vars(1:4), recode) %>%
  mutate_at(vars(5:7), recode2)
df_clean
```

3. The `allowed_column_values` list contains which values are allowed for every column. Try to set all the other values of the columns to `NA`

```{r}
allowed_column_values = list(
  seq(1), 
  seq(2),
  seq(3),
  seq(4),
  seq(5),
  seq(6), 
  seq(7),
  seq(8),
  seq(9),
  seq(10)
) %>%
  set_names(colnames(df))

recode <- function(column, allowed_values) {
  if_else(column %in% allowed_values, column, NA_integer_)
}

names <- colnames(df)
recode(df[[names[1]]], allowed_column_values[[names[1]]])

df_clean <- names %>%
  map(~ recode(df[[.x]], allowed_column_values[[.x]])) %>%
  set_names(names) %>%
  as_data_frame()
df_clean
```

4. Look at the following (not working) code and try to understand what it should do.

```{r, eval=FALSE}
model <- glm(chemneo ~ jaar, data = df, family = binomial(link = 'logit'))
exp(confint(model))
summary(model)

model <- glm(chemneo ~ regio, data = df, family = binomial(link = 'logit'))
exp(confint(model))
summary(model)
```

5. Create an example dataframe that can be used to run this code.
6. Reduce the amount of copy-and-paste by rewriting the code.
7. Use the `broom` package to get the information from the model in a dataframe.

```{r}
df <- tibble(
  "jaar" = 1:10 + 2000,
  "regio" = rep(c("AMS", "UTR"), 5),
  "chemneo" = runif(10)
)

check_variable <- function(col_name) {
  from <- as.formula(paste("chemneo ~", col_name))
  model <- glm(from, data = df, family = binomial(link = 'logit'))
  confint_list <- exp(confint(model))
  list(
    "confint" = confint_list,
    "sum_model" = summary(model)
  )
}

result <- check_variable("jaar")

col_names <- colnames(df)[1:2]
result2 <- map(col_names, check_variable)
result2 <- set_names(result2, col_names)

combn(letters[1:4], 2, simplify = FALSE)
```

