---
title: "Iteration Answers"
output: html_notebook
---

```{r}
library(tidyverse)
load("../../datasets/swapi.rda")
load("../../datasets/planet_lookup.rda")
```

# How many elements are in people?

```{r}
length(people)
```

# Who is the first person in people?

```{r}
people[[1]] # Luke!
```

# What is the difference between people[1] and people[[1]]?

```{r}
people[1] # A list inside a list

people[[1]] # A list, dropped one level of heirachy
```

# How many starships has each character been on?

```{r}
# Do it for 1
length(people[[1]]$starships)

# Put it into a function
count_starships <- function(x) {
  length(x$starships)
}

# Do it for all
map(people, count_starships)
```

# Find the name of each characters homeworld

```{r}
# Do it for 1
planet_lookup[[people[[1]]$homeworld]]

# Put it into a function
get_homeworld <- function(x) {
  planet_lookup[[x$homeworld]]
}

# Do it for all
map(people, get_homeworld)
```

# Combine names of persons with their home planet

```{r}
people <- people %>%
  set_names(map_chr(people, "name"))

map(people, get_homeworld)
```

# How heavy is each person?

```{r}
# Do it for 1
parse_number(people[[1]]$mass, na = "unknown")

# Put it into a function
get_mass <- function(x) {
  parse_number(x$mass, na = "unknown")
}

# Do it for all
map_dbl(people, get_mass)
```

# Which film (see films) has the most characters?

```{r}
map(films, "characters") %>%
  map_int(length) %>%
  set_names(map_chr(films, "title")) %>%
  sort(decreasing = TRUE) %>%
  head(n = 1)
```

# Create the planet_lookup vector from earlier

```{r}
planet_lookup <- map_chr(planets, "name") %>%
  set_names(map(planets, "url"))
```

# Which species has the most possible eye colors?

```{r}
map_chr(species, "eye_colors") %>%
  strsplit(", ") %>%
  map_int(length) %>%
  set_names(map(species, "name"))
# this is lazy, what about n/a and unknown?
```
