---
title: "Function and Iteration Practice Answers"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(gapminder)
library(nycflights13)
# sample dataset to make plots faster
flights <- as_data_frame(flights) %>%
  sample_n(1000)
gapminder <- as_data_frame(gapminder)
```

# Gapminder

1. Make a linear model to predict the `pop`, population, depending on `year` for Afghanistan

```{r}
afg <- gapminder %>%
  filter(country == "Afghanistan")

model <- lm(pop ~ year, afg)
```

2. Get the `r.squared` from this model and the slope.

```{r}
summary(model)$r.squared
coef(model)
```

3. Plot the model and the original data in one graph.

```{r}
ggplot(afg) +
  geom_line(aes(year, pop)) +
  geom_abline(intercept = coef(model)[1], slope = coef(model)[2], color = "red")
```

4. Make a linear model for all the countries and select the 5 with the largest slope and with the lowest `r.squared`

```{r}
nested_gapminder <- gapminder %>%
  group_by(country) %>%
  nest() %>%
  mutate(
    model = map(data, ~lm(pop ~ year, .x)),
    r.squared = map_dbl(model, ~summary(.x)$r.squared),
    slope = map_dbl(model, ~ coef(.x)['year']),
    plot = map2(data, model, ~ ggplot(.x) +
      geom_line(aes(year, pop)) +
      geom_abline(intercept = coef(.y)[1], slope = coef(.y)[2], color = "red")),
    plot = map2(plot, country, ~.x + labs(title = .y))
  )

nested_gapminder %>%
  arrange(desc(slope)) %>%
  head(5) %>%
  pluck("plot")
```

```{r}
nested_gapminder %>%
  arrange(desc(slope)) %>%
  head(5) %>%
  unnest(data) %>%
  ggplot() +
  geom_line(aes(year, pop, color = country))
```

```{r}
nested_gapminder %>%
  arrange(r.squared) %>%
  head(5) %>%
  unnest(data) %>%
  ggplot() +
  geom_line(aes(year, pop, color = country))
```

```{r}
nested_iris <- iris %>%
  group_by(Species) %>%
  nest() %>%
  mutate(
    means = map(data, ~summarise_all(.x, mean))
  )
nested_iris %>%
  unnest(means)
```

1. What if there where 50 columns in your data...

# Flights exploration plots

2. Make a linear model between the priviously mentioned variables and `arr_delay` and select the coefficients of the model with the highst `r.squared`

```{r}
models <- flights %>%
  select(arr_delay, columns) %>%
  gather("key", "value", -arr_delay) %>%
  group_by(key) %>%
  summarise(model = list(glance(lm(arr_delay ~ value)))) %>%
  unnest()
```
