---
title: "Function and Iteration Practice Answers"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(gapminder)
library(nycflights13)
# sample dataset to make plots faster
flights <- as_data_frame(flights) %>%
  sample_n(1000)
gapminder <- as_data_frame(gapminder)
```

# Gapminder

1. Make a linear model to predict the `pop`, population, depending on `year` for Afghanistan

```{r}
afg <- gapminder %>%
  filter(country == "Afghanistan")

model <- lm(pop ~ year, afg)
```

2. Get the `r.squared` from this model and the slope.

```{r}
summary(model)$r.squared
coef(model)
```

3. Plot the model and the original data in one graph.

```{r}
ggplot(afg) +
  geom_line(aes(year, pop)) +
  geom_abline(intercept = coef(model)[1], slope = coef(model)[2], color = "red") +
  labs(title = "Afg")
```

4. Make a linear model for all the countries and select the 5 with the largest slope and with the lowest `r.squared`

```{r}
make_model <- function(data) {
  lm(pop ~ year, data)
}

extract_r_squared <- function(fit) {
  summary(fit)$r.squared
}

extract_slope <- function(fit) {
  coef(fit)[2]
}

plot_fit <- function(data, fit) {
  ggplot(data) +
    geom_line(aes(year, pop)) +
    geom_abline(intercept = coef(fit)[1], slope = coef(fit)[2], color = "red")
}

add_title <- function(plot, input_title) {
  plot + labs(title = input_title)
}

nested_gapminder <- gapminder %>%
  group_by(country) %>%
  nest() %>%
  mutate(
    model = map(data, make_model),
    r_squared = map_dbl(model, extract_r_squared),
    slope = map_dbl(model, extract_slope),
    plot = map2(data, model, plot_fit),
    plot = map2(plot, country, add_title)
  )

nested_gapminder %>%
  arrange(r_squared) %>%
  head(5) %>%
  pluck("plot")
```

```{r}
nested_gapminder %>%
  arrange(desc(slope)) %>%
  head(5) %>%
  unnest(data) %>%
  ggplot() +
  geom_line(aes(year, pop, color = country))
```

```{r}
nested_gapminder %>%
  arrange(r_squared) %>%
  head(5) %>%
  unnest(data) %>%
  ggplot() +
  geom_line(aes(year, pop, color = country))
```

6. Use nest to calculate the mean of all columns per species

```{r}
calc_mean_all_cols <- function(data) {
  summarise_all(data, mean)
}

nested_iris <- iris %>%
  group_by(Species) %>%
  nest() %>%
  mutate(means = map(data, calc_mean_all_cols))

df %>%
  group_by(...) %>%
  nest() %>%
  mutate(... = map(data, .f)) %>%
  unnest()

nested_iris %>%
  unnest(means)
```

# Flights exploration plots

2. Make a linear model between the priviously mentioned variables and `arr_delay` and select the coefficients of the model with the highst `r.squared`

```{r}
library(broom)

columns <- c("dep_time", "sched_dep_time", "arr_time", "sched_arr_time")

fit <- lm(arr_delay ~ dep_time, flights)
glance(fit)

variable <- "dep_time"

make_model <- function(variable) {
  frm <- as.formula(paste("arr_delay ~", variable))
  fit <- lm(frm, flights)
  glance(fit) %>%
    mutate(variable = variable)
}

make_model(flights, columns[1])

tmp <- map_df(columns, make_model)
```

```{r}
make_model <- function(data) {
  lm(arr_delay ~ value, data)
}

models <- flights %>%
  select(arr_delay, columns) %>%
  pivot_longer(-arr_delay, names_to = "name", values_to = "value") %>%
  group_by(name) %>%
  nest() %>%
  mutate(model = map(data, make_model)) %>%
  mutate(scores = map(model, glance)) %>%
  unnest(cols = c(scores))
```

