---
title: "R Notebook Demo"
output:
  html_notebook: default
---

# Heading

## Sub-heading

### Another deeper heading

# Lists

* apples
* oranges
* pears

1. apples
1. oranges
1. pears

# Link

[link](http://www.google.com)

# Options for Chunck

*italic*

**bold**

# Code Visability

## Do not show but run

Typically used for loading packages

```{r, include=FALSE}
library(tidyverse)
library(knitr)
```

## Show both

```{r}
4 + 5
```

## Show only the output

```{r, echo=FALSE}
4 + 5
```

## Shows the code but does not run it

```{r, eval=FALSE}
4 + 5
```

# Outputs

## Variables

The output of a variable shows in the following way:

```{r}
4 + 5
```

This can be presented nicer using inline r:

```{r}
answer <- 4 + 5
```

4 + 5 = **`r answer`**

## Plots

```{r}
ggplot(iris) +
  geom_point(aes(Sepal.Length, Petal.Length, color = Species))  
```

## Tables

### Print a data frame directly

This looks nice in a html format but not really in word or pdf

```{r}
iris
```

### Use the kable package

Looks better in pdf and word

```{r}
iris %>%
  kable()
```
