---
title: "Simpson's paradox"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
UCBAdmissions <- as_data_frame(UCBAdmissions) %>%
  mutate(Admit = factor(Admit, levels = c("Rejected", "Admitted")))
```

Aggregate data on applicants to graduate school at Berkeley for the six largest departments in 1973 classified by admission and sex.

```{r}
UCBAdmissions
```

Plot showing the ratio of rejection for differed genders. This plot suggests a bias in acceptance.

```{r}
ggplot(UCBAdmissions, aes(Gender, n, fill = Admit)) +
  geom_bar(position = "fill", stat = "identity")
```

Plot that shows the ratio of acceptance and rejection per gender per department. This shows that some departments are difficult to get in (C, D, E and especially F) while other are easier (A and B).

```{r}
ggplot(UCBAdmissions, aes(Gender, n, fill = Admit)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_grid(. ~ Dept)
```

Plot that shows the number of people applying to an department per gender. This shows that departments A and B are really popular for males while department C and F are more popular for females.

```{r}
ggplot(UCBAdmissions, aes(Gender, n)) +
  geom_bar(position = "dodge", stat = "identity") +
  facet_grid(. ~ Dept)
```

The conclusion that there is a bias is not valid in this case. A better conclusion is that males apply for easier departments than females.

## Smoking is Healthy?

Data on age, smoking, and mortality from a one-in-six survey of the electoral roll in Whickham, a mixed urban and rural district near Newcastle upon Tyne, in the UK. The survey was conducted in 1972-1974 to study heart disease and thyroid disease. A follow-up on those in the survey was conducted twenty years later.

A data frame with 1314 observations on women for the following variables.

* `outcome` survival status after 20 years: a factor with levels `Alive` `Dead`
* `smoker` smoking status at baseline: a factor with levels `No` `Yes`
* `age` age (in years) at the time of the first survey

```{r}
library(mosaicData)
Whickham <- as_data_frame(Whickham) %>%
  mutate(outcome = factor(outcome, levels = c("Dead", "Alive")))
Whickham
```

The following plot suggests that smoking is healthy because more smokers are still alive. Show if this is a case of the Simpsons paradox or not.

```{r}
ggplot(Whickham) +
  geom_bar(aes(smoker, fill = outcome), position = "fill")
```
