---
title: "lubridate"
author: "Wim van der Ham"
date: "18 de junio de 2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(nycflights13)
library(rlang)
```

Convert the following four columns from the `flights` dataset to a date-time object using `lubridate`.

1. `dep_time`
1. `arr_time`
1. `sched_dep_time`
1. `sched_arr_time`

```{r}
make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

flights_dt <- flights %>% 
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
    sched_dep_time = make_datetime_100(year, month, day, sched_dep_time),
    sched_arr_time = make_datetime_100(year, month, day, sched_arr_time)
  ) %>% 
  select(origin, dest, ends_with("delay"), ends_with("time"))

flights_dt
```

Use the results to show how many flights are leaving every day. Can you identify the difference between specific days of the week?

```{r}
flights_dt %>% 
  ggplot(aes(dep_time)) + 
  geom_freqpoly(binwidth = 86400) # 86400 seconds = 1 day

flights_dt %>% 
  mutate(wd = wday(dep_time, label = TRUE)) %>% 
  ggplot() + 
  geom_bar(aes(wd))
```

Show when the flights left at 2 january 2013.

```{r}
flights_dt %>% 
  filter(date(dep_time) == ymd(20130102)) %>% 
  ggplot() + 
  geom_freqpoly(aes(dep_time), binwidth = 600) # 600 s = 10 minutes
```

Show the `sched_dep_time` of all the flights per minute. Are some minutes more populair for scheduling a flight?

```{r}
flights_dt %>% 
  mutate(minute = minute(sched_dep_time)) %>% 
  group_by(minute) %>% 
  summarise(
    avg_delay = mean(arr_delay, na.rm = TRUE),
    n = n()) %>%
  ggplot() +
  geom_line(aes(minute, n))
```

The next table show flights that have an arrival time that is before the departure time. How is this possible? Fix the error using a time period.

```{r}
flights_dt %>% 
  filter(arr_time < dep_time) 
```

```{r}
flights_dt <- flights_dt %>% 
  mutate(
    overnight = arr_time < dep_time,
    arr_time = arr_time + days(overnight * 1),
    sched_arr_time = sched_arr_time + days(overnight * 1)
  )

flights_dt %>% 
  filter(arr_time < dep_time) 
```
