---
title: "Extra lubridate Exersice Answers"
output: html_notebook
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(nycflights13)

flights <- flights %>%
  sample_n(20000)
```

1. Show the `sched_dep_time` of all the flights per minute. Are some minutes more populair for than others for scheduling a flight?

```{r}
flights %>% 
  mutate(
    sched_dep_time_dt = make_datetime(
      year, month, day, sched_dep_time %/% 100, sched_dep_time %% 100
    ),
    m = minute(sched_dep_time_dt)
  ) %>%
  ggplot() +
  geom_bar(aes(m))
```

2. Group the flights based on `dep_time` and the moment of the day (morning, afternoon, evening, night). Show in a graph the relation between `air_time` and part of the day.

```{r}
flights %>% 
  mutate(
    dep_time_dt = make_datetime(
      year, month, day, dep_time %/% 100, dep_time %% 100
    ),
    day_part = case_when(
      hour(dep_time_dt) < 6 ~ "night",
      hour(dep_time_dt) < 12 ~ "morning",
      hour(dep_time_dt) < 18 ~ "afternoon",
      TRUE ~ "evening"
    )
  ) %>%
  ggplot() +
  geom_boxplot(aes(day_part, air_time))
```

3. First convert both `arr_time` and `dep_time` to a `dttm`. Filter the flights that have an `arr_time` that is before `dep_time`. How is this possible? Fix the error.

```{r}
flights %>% 
  mutate(
    dep_time_dt = make_datetime(
      year, month, day, sched_dep_time %/% 100, sched_dep_time %% 100
    ),
    arr_time_dt = make_datetime(
      year, month, day, arr_time %/% 100, arr_time %% 100
    ),
    overnight = arr_time_dt < dep_time_dt,
    arr_time_dt = arr_time_dt + days(overnight * 1)
  ) %>%
  filter(overnight == TRUE) %>%
  select(dep_time_dt, arr_time_dt)
```
