---
title: "Read data Exersice"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
library(readxl)
```

1. Read the paris_paintings csv.

```{r}
paintings <- read_csv("../../datasets/paris_paintings.csv")
```

2. Read the example excel and save as a csv.

```{r, eval=FALSE}
sheets <- excel_sheets("../../datasets/example_file.xlsx")
excel <- sheets %>%
  map(function(sheet) {
    read_excel("../../datasets/example_file.xlsx", sheet)
  })
excel <- do.call("rbind", excel)
write_csv(excel, "../../datasets/test.csv")
```

3. Read the csv and save as an Rdata file.

```{r, eval=FALSE}
csv <- read_csv("../../datasets/test.csv")
write_rds(csv, "../../datasets/test.Rda")
```

4. Read the Rdata file and check if the information is the same as after reading the excel.

```{r, eval=FALSE}
rds <- read_rds("../../datasets/test.Rda")
```

5. Create your own `tibble` that has 100 rows. The following columns need to be there:

  - **random** A random selection of number between 1 and 10
  - **sequence** A sequence starting from 3 and having steps of 4
  - **rpt** The sequence 1 till 5 repeaded
  - **string** A string value that is the same for all the rows

```{r}
tibble(
  random = sample(1:10, 100, replace = TRUE),
  sequence = seq(3, by = 4, length.out = 100),
  rpt = rep(1:5, 20),
  string = "string"
)
```
