---
title: "Extra Markdown Exersice Answers"
output: html_notebook
---

This file contains some questions to practice the material learned until now. Make sure the result is presentable!

```{r, include=FALSE}
library(tidyverse)
diamonds <- as_tibble(diamonds)
```

1. Show the distribution of the `price` variable in a plot.

```{r}
ggplot(diamonds) +
  geom_histogram(aes(price), binwidth = 400)
```

2. How many diamonts are there per `cut`? Display the result in a graph and a table.

```{r}
diamonds %>%
  group_by(cut) %>%
  summarise(n = n())

diamonds %>%
  count(cut)

ggplot(diamonds) +
  geom_bar(aes(cut))
```

3. Show the relationship between `cut` and the average price per `cut`. Now show this per `carat_group`. This is a varibale you need to create yourself.

```{r}
diamonds %>%
  group_by(cut) %>%
  summarise(mean_price = mean(price)) %>%
  ggplot() +
  geom_bar(aes(cut, mean_price), stat = "identity") 

diamonds %>%
  mutate(carat_group = cut(carat, 5)) %>%
  group_by(cut, carat_group) %>%
  summarise(mean_price = mean(price)) %>%
  ggplot() +
  geom_bar(aes(cut, mean_price, fill = carat_group), 
           stat = "identity", position = "dodge") 
```

4. Give the following statistice of the dataset:
  
```{r}
n_rows <- nrow(diamonds)
avg_price <- round(mean(diamonds$price))
max_price <- max(diamonds$price)
min_price <- min(diamonds$price)
n_cuts <- length(unique(diamonds$cut))
```

  - The number of diamonds: `r n_rows`
  - The average price: `r avg_price`
  - The min price: `r min_price`
  - The max price: `r max_price`
  - The number of `cut`'s: `r n_cuts`