---
title: "Tidy Extra Exersice Answers"
output: html_notebook
---

```{r, include=FALSE}
library(tidyverse)
```

Use the tidy version of the following datasets to answer the nexts questions:

```{r}
weather <- read_csv(
  "../../datasets/weather.csv",
  col_types = list(
    .default = col_integer(),
    id = col_character(),
    element = col_character()
  )
)
pew <- read_csv(
  "../../datasets/pew.csv",
  col_types = list(
    .default = col_double(),
    religion = col_character()
  )
)
```

```{r}
weather_tidy <- weather %>%
  pivot_longer(
    d1:d31, names_to = "day", values_to = "temperature", 
    values_drop_na = TRUE
  ) %>%
  pivot_wider(names_from = "element", values_from = "temperature") %>%
  separate(day, c("d", "day"), sep = 1) %>%
  select(-d, -id) %>%
  mutate(day = as.numeric(day))
```

```{r}
pew_tidy <- pew %>%
  pivot_longer(2:11, names_to = "income", values_to = "count")
```

# weather

1. Calculate the number of days for which we have a measurement per month. And display this in a plot.

```{r}
weather_tidy %>%
  count(month) %>%
  ggplot() +
  geom_bar(aes(factor(month), n), stat = "identity")
```

2. Show in a graph the average min and max temperature per month

```{r}
weather_tidy %>%
  pivot_longer(TMAX:TMIN, names_to = "temptype", values_to = "temp") %>%
  group_by(month, temptype) %>%
  summarise(avg_temp = mean(temp)) %>%
  ggplot() +
  geom_bar(
    aes(x=factor(month), y=avg_temp, fill=temptype), 
    position="dodge", stat="identity"
  ) +
  ylim(0, 400) +
  labs(title = "Average min and max temperature per month", x = "month")


weather_tidy %>%
  group_by(month) %>%
  summarise(avg_min = mean(TMIN),
            avg_max = mean(TMAX)) %>%
  ggplot() +
  geom_point(aes(date_time, TMAX), stat = "identity", color = "blue") +
  geom_point(aes(date_time, TMIN), stat = "identity", color = "red") +
  ylim(0, 400) 
```

# pew

1. Show the percentage of `Don't,know/refused` per religion in a graph.

```{r}
pew_tidy %>%
  group_by(religion) %>%
  mutate(
    total = sum(count),
    perc = count / total * 100
  ) %>%
  filter(income == "Don't,know/refused") %>%
  ggplot() +
  geom_bar(aes(reorder(religion, perc), perc), stat = "identity") +
  coord_flip()
```

2. Show in a graph per income group the percantage of persons from the 3 biggest religions.

```{r}
largest_religions <- pew_tidy %>%
  group_by(religion) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total)) %>%
  slice(1:3) %>%
  pull("religion")

levels <- unique(pew_tidy$income)

pew_tidy %>%
  filter(religion %in% largest_religions) %>%
  mutate(income = factor(income, levels = levels)) %>%
  ggplot() +
  geom_bar(aes(income, count, fill = religion),
           stat = "identity", position = "fill") +
  coord_flip()
```
